Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-12-06 Submission.Rmd
r.version output removed

attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()
R.version
ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1)

>>>>

attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()

ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1)
